Vitae: Aggregated Work Histories for On--Demand Workers

### 2017-07-19 proposals/mediaX/proposal.tex
notes from meeting earlier

\section*{State of the world}
\begin{enumerate}[noitemsep]
  \item Research is showing that both the \textit{breadth} and \textit{depth} (or \textit{complexity})
        of on--demand labor will continue to grow
  \item More people will be doing more kinds of work, transiently moving between myriad platforms
  \item People's educations are becoming increasingly decomposed;
  online education platforms make it possible for people to learn and acquire new skills piecemeal,
  and demonstrate proficiency on ad hoc bases
\end{enumerate}

\section*{Trouble!}
\begin{enumerate}[noitemsep]
  \item The people who enter the workforce in this capacity are increasingly finding that
        this form of work doesn't facilitate the building of more complex, more rewarding work
  \item tracking and \textit{bringing together} the histories of these workers is difficult
  \begin{enumerate}[noitemsep]
    \item it's hard to trust individual workers
    \item platforms don't make it any easier to \textit{amalgamate} data
  \end{enumerate}
\end{enumerate}

\section*{Intuitive solutions (and why they fail)}
\begin{enumerate}[noitemsep]
  \item One solution seems to be to maintain a list of known good workers --- ``whitelisting'' good workers
  \begin{enumerate}[noitemsep]
    \item This generally suffices for large--scale requesters; they form a cohort of known good workers, and
          can (in general) afford to ``explore'' and discover new workers
    \item This solution doesn't work for smaller scale requesters:
    \begin{enumerate}[noitemsep]
      \item Existing requesters don't have much (read: any) incentive to share rosters of good workers
      \item Platforms themselves don't necessarily facilitate sharing in the first place
      \item Small scale requesters don't have sufficient traffic to make it worth it to invest in qualifications exams
      \item Workers who already spend relatively large proportions of their time \textbf{finding tasks}
            don't want to take qualifying exams to become eligible for one--off tasks
    \end{enumerate}
  \end{enumerate}
\end{enumerate}

\section*{Key insight \joke{or ``Wao Such Insight! Much \dots~Insight''}}
\begin{enumerate}[noitemsep]
  \item In our most recent paper, we highlighted some of the common themes between
        the historical piecework and the contemporary ``gig'' or
        on--demand work~\cite{pieceworkCrowdworkGigwork}.
  \item We argued that, while significant differences are to be found throughout the comparisons of
        contemporary cases of on--demand work and historical counterparts,
        these parallel cases can still \textit{inform} how we observe the evolution of work going forward
        and, indeed, how we can shape and design that future.
  \item In that light, we look to the trajectory of piecework in the \nth{20} century for inspiration and find\dots
  \item what about \textbf{hiring halls}? What's important about hiring halls?
  \begin{enumerate}[noitemsep]
    \item Hiring halls were (/are) communities of workers with various skills who band together
          to help dispatch qualified workers for various jobs.
    \item These hiring halls had \textit{de facto} collective bargaining powers.
    \item This was an important step toward collective action and collective governance
          (other topics about which we've written~\cite{dynamo}).
  \end{enumerate}
\end{enumerate}

\section*{What we're building}
\begin{enumerate}[noitemsep]
  \item Building a system that aggregates workers' histories into a single platform
  \item Same with education
  \item Through this, workers can demonstrate their proficiency by accumulating work histories from various platforms
\end{enumerate}

\section*{Why is this hard (or at least not trivial)}
\begin{enumerate}
  \item \ali{All of the reasons we've ever said that the internet complicates offline things}
  \item also, even offline communities of workers are hard to organize;
        we think we can make some of it easier through technology, but \textit{how} is still an open question
\end{enumerate}

>>>>

\ali{Don't be a hundred duck sized horses; be a horse sized duck}

\ali{chekhov's gun; don't put something in the story if you won't advance it to the end (or very far)}

\section*{State of the world}
\begin{enumerate}[noitemsep]
  \item Research is showing that both the \textit{breadth} and \textit{depth} (or \textit{complexity})
        of on--demand labor will continue to grow
  \item More people will be doing more kinds of work, transiently moving between myriad platforms \ali{more quickly than before}
  \ali{relationships are shrinking to the span of a few minutes, and people may only interact once}
  \item People's educations are becoming increasingly decomposed;
  online education platforms make it possible for people to learn and acquire new skills piecemeal,
  and demonstrate proficiency on ad hoc bases
\end{enumerate}

\section*{Trouble!}
\begin{enumerate}[noitemsep]
  \item \ali{silo'ing} The people who enter the workforce in this capacity are increasingly finding that
        this form of work doesn't facilitate the building of more complex, more rewarding work
  \item tracking and \textit{bringing together} the histories of these workers is difficult
  \begin{enumerate}[noitemsep]
    \item it's hard to trust individual workers
    \item platforms don't make it any easier to \textit{amalgamate} data
  \end{enumerate}
\end{enumerate}

\section*{Intuitive solutions (and why they fail)}
\begin{enumerate}[noitemsep]
  \item \ali{feel free to jump around \msb{jump, jump, jump around}, like pointing to preference of freelancers; just say that this is a wider phenomenon}
  \item \ali{find some econ literature or something that finds that people prefer workers they know (i.e. gravitate toward whitelisting)}
  \item One solution seems to be to maintain a list of known good workers --- ``whitelisting'' good workers
  \begin{enumerate}[noitemsep]
    \item This generally suffices for large--scale requesters; they form a cohort of known good workers, and
          can (in general) afford to ``explore'' and discover new workers
    \item This solution doesn't work for smaller scale requesters:
    \begin{enumerate}[noitemsep]
      \item Existing requesters don't have much (read: any) incentive to share rosters of good workers
      \item Platforms themselves don't necessarily facilitate sharing in the first place
      \item Small scale requesters don't have sufficient traffic to make it worth it to invest in qualifications exams
      \item Workers who already spend relatively large proportions of their time \textbf{finding tasks}
            don't want to take qualifying exams to become eligible for one--off tasks
    \end{enumerate}
  \end{enumerate}
\end{enumerate}

\section*{Key insight \joke{or ``Wao Such Insight! Much \dots~Insight''}}
\begin{enumerate}[noitemsep]
\item \ali{don't be too meta; just cite the \textit{idea} of a hiring hall}
  \item In our most recent paper, we highlighted some of the common themes between
        the historical piecework and the contemporary ``gig'' or
        on--demand work~\cite{pieceworkCrowdworkGigwork}.
  \item We argued that, while significant differences are to be found throughout the comparisons of
        contemporary cases of on--demand work and historical counterparts,
        these parallel cases can still \textit{inform} how we observe the evolution of work going forward
        and, indeed, how we can shape and design that future.
  \item In that light, we look to the trajectory of piecework in the \nth{20} century for inspiration and find\dots
  \item what about \textbf{hiring halls}? What's important about hiring halls?
  \begin{enumerate}[noitemsep]
    \item Hiring halls were (/are) communities of workers with various skills who band together
          to help dispatch qualified workers for various jobs.
    \item These hiring halls had \textit{de facto} collective bargaining powers.
    \item This was an important step toward collective action and collective governance
          (other topics about which we've written~\cite{dynamo}).
  \end{enumerate}
  \item \ali{aggregating workers histories to make it possible to communicate skills}
  \item \ali{hiring halls had to be \textbf{bottlenecks}; we can be less bottlenecky}
\end{enumerate}

\section*{What we're building}
\begin{enumerate}[noitemsep]
\item \ali{be more concrete about what the system will do}
\item \ali{maybe make a nice--looking figure}
  \item Building a system that aggregates workers' histories into a single platform
  \item Same with education
  \item Through this, workers can demonstrate their proficiency by accumulating work histories from various platforms
\end{enumerate}

\section*{Why is this hard (or at least not trivial)}
\begin{enumerate}

  \item \ali{All of the reasons we've ever said that the internet complicates offline things}
  \item also, even offline communities of workers are hard to organize;
        we think we can make some of it easier through technology, but \textit{how} is still an open question
\end{enumerate}

\ali{evaluation plan?}

\ali{so what/impact of outcome}
